working title Compatibility system and stigma size are the main predictors of heterospecific pollen effect

### 2019-03-05 Manuscript_draft/Manuscript_draft.Rmd
edits

\newpage
```{r, echo=FALSE, message=FALSE, warning=FALSE,cache=FALSE,fig.height=6,fig.width=6,fig.cap="A"}

>>>>

\newpage
```{r, echo=FALSE, message=FALSE, warning=FALSE,cache=FALSE,fig.height=6,fig.width=6,fig.cap="Average effect size and confidence intervals (95%) of the 9 heterospecific treatments of 50% pollen to the different 10 focal species."}

### 2019-03-05 Manuscript_draft/Manuscript_draft.tex
edits
Edits

\begin{figure}
\centering
\includegraphics{output/figures/unnamed-chunk-2-1.pdf}
\caption{A}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{output/figures/unnamed-chunk-4-1.pdf}
\caption{Effect sizes for the 10 different species. The different
families appear with different colours, when a species was focal was
coloured differently from its family.}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{output/figures/unnamed-chunk-5-1.pdf}
\caption{A}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{output/figures/unnamed-chunk-6-1.pdf}
\caption{The effect of heterospecific pollen (scaled see set) is
represented in function of the compatibility system (self/cross*100) for
the the different species. Each coulored dot represents the interaction
of a focal species with a different pollen donor.}
\end{figure}

@@

\includegraphics{output/figures/unnamed-chunk-8-1.pdf}
\includegraphics{output/figures/unnamed-chunk-8-2.pdf}
\includegraphics{output/figures/unnamed-chunk-8-3.pdf}

>>>>

\begin{figure}
\includegraphics[width=1\linewidth]{images/phylo_image} \caption{Phylogenetic tree of the ten species used in the experiment from three different families from bottom to top: Solanaceae, Convolvulaceae and Brassicaceae.}\label{fig:unnamed-chunk-2}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{output/figures/unnamed-chunk-4-1.pdf}
\caption{Average effect size and confidence intervals (95\%) of the 9
heterospecific treatments of 50\% pollen to the different 10 focal
species}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{output/figures/unnamed-chunk-5-1.pdf}
\caption{Effect sizes for the 10 different species. The different
families appear with different colours, when a species was focal was
coloured differently from its family.}
\end{figure}

\begin{figure}
\centering
\includegraphics{output/figures/unnamed-chunk-6-1.pdf}
\caption{A}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{output/figures/unnamed-chunk-7-1.pdf}
\caption{The effect of heterospecific pollen (scaled see set) is
represented in function of the compatibility system (self/cross*100) for
the the different species. Each coulored dot represents the interaction
of a focal species with a different pollen donor.}
\end{figure}

@@

\includegraphics{output/figures/unnamed-chunk-9-1.pdf}
\includegraphics{output/figures/unnamed-chunk-9-2.pdf}
\includegraphics{output/figures/unnamed-chunk-9-3.pdf}
